---
title: "EDA_stat"
author: "Seunghoon Yang"
date: "2022-10-15"
output: html_document
---

Through the two datasets, I would like to verify that Busan, Ulsan, Gyeongnam, and Seoul have regional variations in admission, employment, and maintenance of employment status of female engineering personnel.

### Loading Packages

```{r setup}
library(tidyverse)
library(readxl)

```


### Loading Datasets
The first dataset is "학교 학과별 데이터넷" for understanding the numbers and ratio of female students. It is imported from 'https://kess.kedi.re.kr/index'.

The second dataset is "산업기술인력 실태조사" for understanding the numbers and ratio of female engineers in the field. It is imported from 'https://kosis.kr/statisticsList/statisticsListIndex.do?menuId=M_01_01&vwcd=MT_ZTITLE&parmTabId=M_01_01&outLink=Y&parentId=D.1;D_18.2;#D_18.2'

``` {r loading_stats, message = FALSE, warning = FALSE}

edustat <- read_excel("../datasets/edustat_부울경.xlsx")
files_list <- list.files(path = "../datasets", pattern = "*.xlsx")[-1]
df_list <- map(str_c("../datasets/", files_list), read_excel, skip = 1)
industry <- bind_rows(df_list) %>% 
  fill(시점) %>% 
  mutate(지역 = c(rep("부산", 316), rep("경남", 320), rep("서울", 302), rep("울산", 294))) %>% 
  mutate_at(3:44, as.numeric)


head(edustat)
head(industry)

```

### Some Wrangling

``` {r wrangling}
edustat_seoul <- edustat %>% 
  filter(시도 == "서울" & 대계열 == "공학계열")

edustat_gn <- edustat %>% 
  filter(시도 == "경남" & 대계열 == "공학계열")
edustat_bsn <- edustat %>% 
  filter(시도 == "부산" & 대계열 == "공학계열")
edustat_usn <- edustat %>% 
  filter(시도 == "울산" & 대계열 == "공학계열")

edustat_sum_seoul <- edustat_seoul %>% 
  group_by(year, 중계열, 과정구분) %>% 
  summarize(졸업자_남자_비중 = mean(졸업자중남자, na.rm = TRUE),
            졸업자_여자_비중 = mean(졸업자중여자, na.rm = TRUE),
            취업자_남자_비중 = mean(취업자중남자, na.rm = TRUE),
            취업자_여자_비중 = mean(취업자중여자, na.rm = TRUE),
            전체_취업률 = mean(취업률_계, na.rm = TRUE),
            남자_취업률 = mean(남자취업률, na.rm = TRUE),
            여자_취업률 = mean(여자취업률, na.rm = TRUE))

edustat_sum_gn <- edustat_gn %>% 
  group_by(year, 중계열, 과정구분) %>% 
  summarize(졸업자_남자_비중 = mean(졸업자중남자, na.rm = TRUE),
            졸업자_여자_비중 = mean(졸업자중여자, na.rm = TRUE),
            취업자_남자_비중 = mean(취업자중남자, na.rm = TRUE),
            취업자_여자_비중 = mean(취업자중여자, na.rm = TRUE),
            전체_취업률 = mean(취업률_계, na.rm = TRUE),
            남자_취업률 = mean(남자취업률, na.rm = TRUE),
            여자_취업률 = mean(여자취업률, na.rm = TRUE))

edustat_sum_bsn <- edustat_bsn %>% 
  group_by(year, 중계열, 과정구분) %>% 
  summarize(졸업자_남자_비중 = mean(졸업자중남자, na.rm = TRUE),
            졸업자_여자_비중 = mean(졸업자중여자, na.rm = TRUE),
            취업자_남자_비중 = mean(취업자중남자, na.rm = TRUE),
            취업자_여자_비중 = mean(취업자중여자, na.rm = TRUE),
            전체_취업률 = mean(취업률_계, na.rm = TRUE),
            남자_취업률 = mean(남자취업률, na.rm = TRUE),
            여자_취업률 = mean(여자취업률, na.rm = TRUE))

edustat_sum_usn <- edustat_usn %>% 
  group_by(year, 중계열, 과정구분) %>% 
  summarize(졸업자_남자_비중 = mean(졸업자중남자, na.rm = TRUE),
            졸업자_여자_비중 = mean(졸업자중여자, na.rm = TRUE),
            취업자_남자_비중 = mean(취업자중남자, na.rm = TRUE),
            취업자_여자_비중 = mean(취업자중여자, na.rm = TRUE),
            전체_취업률 = mean(취업률_계, na.rm = TRUE),
            남자_취업률 = mean(남자취업률, na.rm = TRUE),
            여자_취업률 = mean(여자취업률, na.rm = TRUE))

industry_subset <- industry %>% 
  mutate(여성비율 = `학사(여)` / 학사) %>% 
  rename(산업별 = `산업별(1)`) %>% 
  filter(산업별 %in% c("기계", "디스플레이", "반도체", "섬유", "자동차", "전자", "철강", "화학", "바이오ㆍ헬스"))

```

### Visualization and Summary Stats

```{r summ}

library(extrafont)
theme_set(theme_gray(base_family='AppleGothic'))

edustat_sum_gn %>% filter(과정구분 == "대학과정") %>% 
  ggplot(aes(x = year, y = 여자_취업률)) +
  geom_line(aes(color = 중계열, group = 중계열))

industry_subset %>% 
  group_by(지역, 산업별) %>% 
  summarize(여성비율 = mean(여성비율))

```