---
title: "HW_class6"
author: "Seunghoon Yang"
date: "2022-10-30"
output: html_document
---

# 1. Data Structure

## Preparing: Load packages and data.

```{r load_package}

library(tidyverse)
library(quanteda)
library(quanteda.textplots)

mixer<-read.csv("../datasets/Homework_Mixerdata.csv", header=T, na.strings=c("","NA")) #If blank, make it NA
table(is.na(mixer))
mixer_complete<-na.omit(mixer) #let's just use the complete cases only 

```

## Tokenizing and text data-wrangling

```{r wrangling}

view_complete_tasks <- mixer_complete$View1 %>% tokens(what = "word",
                                                       remove_punct = TRUE,
                                                       remove_numbers = TRUE,
                                                       remove_separators = TRUE,
                                                       remove_symbols = TRUE) %>% 
  tokens_tolower() %>% 
  tokens_remove(stopwords('english')) %>% 
  tokens_wordstem() %>% 
  dfm() %>% 
  dfm_trim(min_docfreq = 0.1,
           max_docfreq = 0.95,
           docfreq_type = 'prop')

mixer_features<-as.data.frame(featfreq((view_complete_tasks)))
colnames(view_complete_tasks)

names(mixer_features)[names(mixer_features) == 'featfreq((view_complete_tasks))'] <- 'freq'

mixer_features<-tibble::rownames_to_column(mixer_features, "feature")

mixer_ordered<-mixer_features %>% arrange(-(freq))
head(mixer_ordered)
```

# 2. Understanding Structure and Descriptive statistics

```{r descriptive_stat}

ndoc(view_complete_tasks)
nfeat(view_complete_tasks)

#frequent features
topfeatures(view_complete_tasks, 20)

#10 least frequent features
topfeatures(view_complete_tasks, decreasing=F, 20)
```

## Wordcloud and SNA graphs

```{r plots}
# Wordcloud
textplot_wordcloud(view_complete_tasks, max_words=50, color="grey10")

# co-currence
mixer_fcm <- fcm(view_complete_tasks)
mixer_fcm

mixer_fcm_plotdata <- fcm_select(mixer_fcm,
                                 pattern = c("bosch", "lid", "jar", "time", "clean", "one", "get"),
                                 selection = "keep")
textplot_network(mixer_fcm_plotdata)

df <- convert(mixer_fcm, to = "data.frame")

df

```

# 3. Methods

This article contains QCA(Qualitative Content Analysis) of a Mixer review data in India. The data was extracted from amazon.com. The dataset has seven variables and 1191 observations. For doing data analysis efficiently, this research omits the 864 observations that contain any NAs. QCA method transforms qualitative data to the observation value of columns in a tabular dataset with tokenization. Tokenization uses some dictionary and grammar as a method. After tokenizing, researchers can use qualitative data for descriptive statistics, inference statistics, network analysis, etc. 

In this study, I'll tokenize View1 variable and see the descriptive statistics from the word count, plot them as word clouds and some bar plots, and conduct network analysis with the Feature co-occurrence matrix. After doing them, I'll figure out the most and least frequent words and the relationships among terms (stemmed).