---
title: "li_chapter2"
author: "Seunghoon Yang"
date: "2022-10-14"
output: html_document
---

### Setup (load packages and data)
I'll use 'tidyverse' package because it contains ggplot2 and some useful data-wrangling packages.

```{r load_package_data}
library(tidyverse)
pwt7 <- read.csv("../datasets/pwt70_w_country_names.csv",
                 header = TRUE, stringsAsFactors = FALSE, strip.white = TRUE, na.strings = c("NA", ""))

```

### Seeing the structure of dataset pwt7

```{r structure_data}

# inspect dataset pwt7
#View(pwt7)

# first observation of dataset pwt7
pwt7 %>% 
  head(1)

# last observation of dataset pwt7
pwt7 %>% 
  tail(1)

# dimensions of dataset pwt7
pwt7 %>% 
  dim()

# column names of dataset pwt7
pwt7 %>% 
  names()

# structure of dataset pwt7
str(pwt7)


```

### Drawing R Basic Graphs

``` {r basic graphs}

par(mfrow=c(2,2))

hist(pwt7$rgdpl)
boxplot(pwt7$rgdpl)
qqnorm(pwt7$rgdpl)


```

### Indexing

``` {r indexing}

### most simple indexing
pwt7$POP[5]

### indexing with some conditions
pwt7$POP[pwt7$country == "Afghanistan" & pwt7$year == 1954]
### pipe-operator way
pwt7 %>% 
  filter(country == "Afghanistan" & year == 1954) %>% 
  .$POP

### indexing row number and column number
pwt7[5, 4]

### indexing row number with column name
pwt7[pwt7$country == "Afghanistan" & pwt7$year == 1954, "POP"]

```

### Ordering / Sorting

``` {r sorting}

# sort data first by country and then by year
pwt7 <- pwt7[order(pwt7$country, pwt7$year), ]
# sort data first by country and then by year (descending)
pwt7 <- pwt7[order(pwt7$country, -pwt7$year), ]


```

### Slicing or Selecting

``` {r slicing}

### selecting rows
pwt7[c(100, 102), ]
### selecting columns
pwt7[, c("country", "year", "rgdpl")] %>% 
  head(10)

### dplyr and magrittr way
pwt7 %>% 
  .[c(100, 102), ]

pwt7 %>% 
  select(country, year, rgdpl) %>% 
  head(10)

### selecting rows and columns
pwt7 %>% 
  .[c(100, 102), c("country", "year", "rgdpl")]

pwt7 %>% 
  .[pwt7$year >= 2006 & pwt7$country == "Afghanistan", c("country", "year", "rgdpl")]

pwt7 %>% 
  .[c(100, 102), ] %>% 
  select(country, year, rgdpl)

# outputs are as same as above but I'm using filter and select from dplyr and subset from baseR.
pwt7 %>% 
  filter(year >= 2006 & country == "Afghanistan") %>% 
  select(country, year, rgdpl)

pwt7 %>% 
  subset(year >= 2006 & country == "Afghanistan", select = c(country, year, rgdpl))

# selecting multiple countries and non-consecutive years
pwt7 %>% 
  filter(year %in% c(1970, 1980, 1990, 2000, 2009) & country %in% c("India", "China Version 1")) %>% 
  select(country, year, rgdpl)

```

### Create a new Dataset with Subset of Data

``` {r subsett}

pwt7new <- pwt7 %>% select(country, year, rgdpl)

pwt7_tmp1 <- pwt7 %>% select(isocode, year, rgdpl)
pwt7_tmp2 <- pwt7 %>% select(isocode, year, openk)

pwt7_m <- merge(pwt7_tmp1, pwt7_tmp2, by = c("isocode", "year"), all = TRUE, sort = TRUE)
#dplyr way
pwt7_m2 <- pwt7_tmp1 %>% 
  left_join(pwt7_tmp2, by = c("isocode", "year"))

# creating a subset of pwt7 (india, pakistan, three variables)
pwt7_ip <- pwt7 %>% 
  filter(year %in% c(1950, 1960, 1970, 1980, 1990, 2000) & country %in% c("India", "Pakistan")) %>% 
  select(country, year, rgdpl)

pwt7_ip

# long to wide form
pwt7_ip2 <- pwt7_ip %>% 
  pivot_wider(names_from = country, values_from = rgdpl)

pwt7_ip2

pwt7_ip2 %>% 
  pivot_longer(cols=India:Pakistan, names_to = "country", values_to = "rgdpl") %>% 
  arrange(country, year)

```

## Manage Observations in magrittr & dplyr ways

``` {r observations}

pwt7_nc <- pwt7 %>% filter(isocode != "CH2")

pwt7 %>% filter(isocode == "CH2") %>% 
  .$year

pwt7_nc %>% filter(isocode == "CH2") %>% 
  .$year

pwt7_dup <- pwt7_ip %>% bind_rows(pwt7_ip %>% filter(country == "India"))
pwt7_dup

# remove duplicated rows
pwt7_dup[!duplicated(pwt7_dup %>% select("country", "year")), ]

```

## Manage Variables

``` {r variables}

# create real per capita investment in 2005 international $
pwt7$investpc <- pwt7$rgdpl * pwt7$ki / 100

# create total real investment in 2005 international $
pwt7$invest <- pwt7$rgdpl * pwt7$POP * pwt7$ki * 10

```

### create a character variable income_group

``` {r income_group}

pwt7 <- pwt7 %>% 
  mutate(income_group = case_when(rgdpl <= 1000 ~ "low_income",
                                  rgdpl > 1000 & rgdpl < 4000 ~ "low_middle",
                                  rgdpl > 4000 & rgdpl < 12000 ~ "up_middle",
                                  rgdpl > 12000 ~ "high_income",
                                  TRUE ~ as.character(NA)))

class(pwt7$income_group)

pwt7 <- pwt7 %>% 
  mutate(income_group = parse_factor(income_group, 
                                     levels = c("low_income", "low_middle", "up_middle", "high_income"), ordered = TRUE))

# making income_group with numbers
pwt7 <- pwt7 %>% 
  mutate(income_group2 = case_when(rgdpl <= 1000 ~ 1,
                                   rgdpl > 1000 & rgdpl < 4000 ~ 2,
                                   rgdpl > 4000 & rgdpl < 12000 ~ 3,
                                   rgdpl > 12000 ~ 4))

class(pwt7$income_group2)

# labeling with factor function
pwt7 <- pwt7 %>% 
  mutate(income_group2 = factor(income_group2,
                                      labels = c("low_income", "low_middle", "up_middle", "high_income")))

# create a chracter variable for decade
pwt7 <- pwt7 %>% 
  mutate(decade = case_when(year >= 1950 & year < 1960 ~ "1950s", 
                            year >= 1960 & year < 1970 ~ "1960s",
                            year >= 1970 & year < 1980 ~ "1970s",
                            year >= 1980 & year < 1990 ~ "1980s",
                            year >= 1990 & year < 2000 ~ "1990s",
                            year >= 2000 ~ "2000s"))

table(pwt7$decade)
```

### Leading, Lagged, and Growth Rate Variables

```{r llgr_var}

# sort data by country and then by year
pwt7 <- pwt7 %>% 
  arrange(country, year)

# Make Growth Rate Variables with Lead and Lag variables
pwt7 <- pwt7 %>% 
  arrange(country, year) %>% 
  mutate(rgdplead = lead(rgdpl, n = 1L, order_by = country),
         rgdplag = lag(rgdpl, n = 1L, order_by = country),
         growth = (rgdpl-rgdplag)/rgdplag)
# aggregate way
pwt7_ag <- aggregate(growth ~ decade + income_group, data = pwt7, FUN=mean)
pwt7_ag

# dplyr way
pwt7_ag2 <- pwt7 %>% 
  group_by(decade, income_group) %>% 
  summarize(mean_growth = mean(growth, na.rm=TRUE)) %>% 
  na.omit(income_group) %>% 
  arrange(income_group)

# merging
pwt7 <- pwt7 %>% 
  left_join(pwt7_ag2, by = c("decade", "income_group"))

# summarizing multiple criteria with multiple variables
pwt7_cs <- pwt7 %>% 
  group_by(isocode, decade) %>% 
  summarize(growth_mean = mean(growth, na.rm = TRUE), openk_mean = mean(openk, na.rm = TRUE), pop_mean = mean(POP, na.rm = TRUE),
            growth_sd = sd(growth, na.rm = TRUE), openk_sd = sd(openk, na.rm = TRUE), pop_sd = sd(POP, na.rm = TRUE))

tail(pwt7_cs, 1)

# renaming variables
pwt7 <- pwt7 %>% 
  rename(population = POP)

names(pwt7)

# recode names
pwt7 %>% 
  mutate(isocode = recode(isocode, "CH2"= "CHN"),
         country = recode(country, "China Version 1" = "China")) -> pwt7

pwt7$rgdpl[pwt7$rgdpl == -999] <- NA
```

### Labelling

```{r labelling}
library(Hmisc)
label(pwt7)

label(pwt7$isocode) <- "Penn World Table country code"
label(pwt7$rgdpl) <- "PPP Converted GDP Per Capita (Laspeyres) derived from growth rates of c, g, i, at 2006 constant prices"
label(pwt7$openk) <- "Openness at 2006 constant prices in percent"
label(pwt7$population) <- "Population (in thousands)"
label(pwt7$growth) <- "annual economic growth rate, based on RGDPL"

label(pwt7)
```