---
title: "2nd Homework (STP702)"
author: "Seunghoon Yang"
date: "2022-09-23"
output: html_document
---

### Get the working directory 
But I don't need to setup a different working directory because I built a project folder using the project function of RStudio.
```{r}

getwd()
library(tidyverse)

```

### Create a Vector Using c() function
```{r}
c(1, 2, 0, 2, 4, 5, 10, 1)

v1 <- c(1, 2, 0, 2, 4, 5, 10, 1)
v1

class(v1)
```

### Calculate Descriptive Statistics for A Vector
```{r}

length(v1) # size of a sample / number of observations

mean(v1)
sum(v1) / length(v1) ### so-called average/mean

var(v1)
sum((v1-mean(v1))^2) / (length(v1)-1) # sample variance

sd(v1)
sqrt(var(v1)) # sample's standard deviation

max(v1) # sample's maximum observation value
min(v1) # sample's minimum observation value

```

### Handle Missing Values in Descriptive Statistics

```{r}
v2 <- c(1, 2, 0, 2, NA, 5, 10, NA)
mean(v2)

# compute mean after removing NA values
mean(v2, na.rm = TRUE)

# display output from is.na() function
is.na(v2)

# display output from !is.na() function
!is.na(v2)

# find total number of observations in v2
length(v2)

# find the number of missing values in v2
sum(is.na(v2))

# find the number of non-missing values in v2
sum(!is.na(v2))
```

### Convert a vector to a data-frame

```{r}

vd <- data.frame(v1)
vd

vd <- data.frame(v1, v2)
vd

```

### Simple Toy Program: Create, Describe, and Graph a Variable

```{r}
c(1, 2, 0, 2, 4, 5, 10, 1)

v1 <- c(1, 2, 0, 2, 4, 5, 10, 1)

# call v1 to see what is it in
v1

# identify object type of v1
class(v1)

# load stargazer package
library(stargazer)

stargazer(vd, type = 'text')

stargazer(vd, type = 'text', summary = FALSE, rownames = FALSE)

stargazer(vd, type = 'text', median = TRUE, rownames = TRUE)

stargazer(vd, type = 'text', median = TRUE, iqr = TRUE)

stargazer(vd, type = 'text', summary.stat = c("n", "mean", "median", "sd"))

stargazer(vd, type = 'text', summary.stat = c('n', 'mean', 'sd', 'min', 'p25', 'median', 'p75', 'max'))


# graph the distribution of variable
# display the frequency count of v1 in vd

table(vd$v1)

# graph the distribution of discrete variable vd$v1 : bar chart
barplot(vd$v1)
ggplot(vd, aes(x = v1)) + geom_bar()
hist(vd$v1)

# graph the distribution of continuous variable vd$c1:

barplot(vd$v1)
hist(vd$v1)

```

### Simple Real-World Example: Data from Iversen and Soskice (2006)

``` {r}

country <- c("Australia", "Austria", "Belgium", "Canada", "Denmark", "Finland", "France", "Germany", "Ireland", "Italy", "Japan",
             "Netherland", "New Zealand", "Norway", "Sweden", "U.K.", "US")

gini.red <- c(23.97, NA, 35.56, 21.26, 37.89, 35.17, 25.36, 18.7, NA, 12.13, NA, 30.59, NA, 27.52, 37.89, 22.67, 17.6)

wage.ineq <- c(1.7, NA, 1.64, 1.82, 1.58, 1.68, 1.94, 1.7, NA, 1.63, NA, 1.64, NA, 1.5, 1.58, 1.78, 2.07)

pr <- c(0, 1, 1, 0, 1, 1, 0, 1, 0, 1, 0, 1, 0, 1, 1, 0, 0)

is2006apar <- data.frame(country, gini.red, wage.ineq, pr)

is2006apar

stargazer(is2006apar, type = 'text', title = 'Summary Statistics', 
          median = TRUE, covariate.labels = c("GINI reduction", "wage inequality", "PR system"))

# graph distribution of wage inequality
boxplot(is2006apar$wage.ineq)
hist(is2006apar$wage.ineq)

# graph distribution of electoral system variable pr
barplot(table(is2006apar$pr))

```

### How to export R output to a File

``` {r}

sink("output.txt")

c(1, 2, 0, 2, 4, 6, 10, 1)

v1 <- c(1, 2, 0, 2, 4, 6, 10, 1)

v1

sink()

```

### How to Save a Graph into a File of pdf or Other Formats

``` {r}

pdf("graph.pdf")

hist(v1)

dev.off()

# create image files of alternative formats

bmp("graph1.bmp")
jpeg("graph1.jpg")
png("graph1.png")
postscript("graph1.ps")

```

### Exercise

``` {r}

#1.3
total_data <- tibble(redistribution = c(23.97, NA, 35.56, 21.26, 37.89, 35.17, 25.36, 18.70, NA, 12.13, NA, 30.59, NA, 27.52, 37.89, 22.67, 17.60),
                     inequality = c(1.70, NA, 1.64, 1.82, 1.58, 1.68, 1.94, 1.70, NA, 1.63, NA, 1.64, NA, 1.50, 1.58, 1.78, 2.07),
                     partisanship = c(0.47, 0.30, 0.36, 0.36, 0.35, 0.30, 0.40, 0.39, 0.42, 0.37, 0.78, 0.31, 0.43, 0.15, 0.17, 0.52, 0.40),
                     votor_turmoil = c(84, 87, 88, 68, 84, 79, 66, 81, 75, 93, 71, 85, 85, 80, 84, 76, 56),
                     unionization = c(46, 54, 48, 30, 67, 53, 18, 34, 48, 34, 31, 33, 23, 54, 67, 42, 23),
                     veto_points = c(3, 1, 1, 2, 0, 1, 1, 4, 0, 1, 1, 1, 0, 0, 0, 0, 5),
                     electoral_system = c(0, 1, 1, 0, 1, 1, 0, 1, 0, 1, 0, 1, 0, 1, 1, 0, 0),
                     left_fragmentation = c(-0.39, -0.18, -0.34, 0.18, -0.40, -0.18, 0.10, -0.13, -0.33, 0.20, 0.22, 0.18, -0.40, -0.02, -0.40, 0.08, 0),
                     right_over_rep = c(0.10, 0.04, 0.27, -0.11, 0.07, 0.09, 0.09, 0.15, 0.70, 0.08, 0.28, -0.36, 0.98, -0.32, -0.03, 0.07, -0.17),
                     per_capita_income = c(10909, 8311, 8949, 11670, 9982, 8661, 9485, 9729, 5807, 7777, 7918, 9269, NA, 9863, 9982, 9282, 13651),
                     female_labor_participation = c(46, 51, 43, 48, 63, 66, 51, 51, 37, 38, 56, 35, 47, 52, 63, 54, 53),
                     unemploy = c(4.63, 2.76, 7.89, 6.91, 6.83, 4.48, 4.57, 4.86, 9.09, 8.12, 1.77, 4.62, NA, 2.28, 6.83, 5.01, 5.74))

total_data


#1.4

stargazer(is2006apar, type = 'text', title = 'Summary Statistics', 
          median = TRUE, covariate.labels = c("GINI reduction", "wage inequality", "PR system"))


#1.5

par(mfrow = c(1, 2))

boxplot(is2006apar$wage.ineq)
hist(is2006apar$wage.ineq)

#1.6

boxplot(total_data$inequality)
boxplot(total_data$electoral_system)


#1.7



```