---
title: "2nd Homework (STP702)"
author: "Seunghoon Yang"
date: "2022-09-23"
output: html_document
---

### Get the working directory 
But I don't need to setup a different working directory because I built a project folder using the project function of RStudio.
```{r}

getwd()

```

### Create a Vector Using c() function
```{r}
c(1, 2, 0, 2, 4, 5, 10, 1)

v1 <- c(1, 2, 0, 2, 4, 5, 10, 1)
v1

class(v1)
```

### Calculate Descriptive Statistics for A Vector
```{r}

length(v1) # size of a sample / number of observations

mean(v1)
sum(v1) / length(v1) ### so-called average/mean

var(v1)
sum((v1-mean(v1))^2) / (length(v1)-1) # sample variance

sd(v1)
sqrt(var(v1)) # sample's standard deviation

max(v1) # sample's maximum observation value
min(v1) # sample's minimum observation value

```

### Handle Missing Values in Descriptive Statistics

```{r}
v2 <- c(1, 2, 0, 2, NA, 5, 10, NA)
mean(v2)

# compute mean after removing NA values
mean(v2, na.rm = TRUE)

# display output from is.na() function
is.na(v2)

# display output from !is.na() function
!is.na(v2)

# find total number of observations in v2
length(v2)

# find the number of missing values in v2
sum(is.na(v2))

# find the number of non-missing values in v2
sum(!is.na(v2))
```

### Convert a vector to a data-frame

```{r}

vd <- data.frame(v1)
vd

vd <- data.frame(v1, v2)
vd

```

### Simple Toy Program: Create, Describe, and Graph a Variable

```{r}
c(1, 2, 0, 2, 4, 5, 10, 1)

v1 <- c(1, 2, 0, 2, 4, 5, 10, 1)

# call v1 to see what is it in
v1

# identify object type of v1
class(v1)
```